Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-22 revise/revise.tex
spaces before citations

        More recently, Aufiero et al. \cite{aufiero_development_2014} have 
        begun to
        approach transient simulations in the MSFR within the finite 
        volume
        OpenFOAM multiphysics toolkit\cite{weller_tensorial_1998}.  This 
        approach
        benefits from pre-implemented turbulence models available in the 
        OpenFOAM
        library and captures the full-core three-dimensional geometry of the 
        reactor
        primary circuit.  OpenFOAM CFD has additionally been shown by 
        Laureau et
        al. \cite{laureau_transient_2017} to couple well with Transient Fission 
        Matrix
        neutronics within the MSFR.
\end{solution}

@@

\question Concerning the openness of the code and the possibility to contribute to it, it should be noted that codes solving for neutron transport can be subject to export restrictions (following their potential dual use), and in principle all contributors should get an export control authorization from their own country. The authors are not strictly required to change the manuscript, but they may consider mentioning the fact that the openness of a nuclear code can be somewhat thwarted by national and international laws.
\begin{solution}
	Excellent point. We have added the following text: ``While export
control laws have the potential to restrict openness of neutron transport
software that is dual use, there is no reason to believe that Moltres could be
used for weapons proliferation.  Moltres requires that cross sections be
provided by the user, implements a combination of algorithms that can be easily
derived from open literature, is tailored to molten salt reactor physics.
Accordingly, Moltres joins a veritable parade of open academic nuclear
engineering software such as OpenMC\cite{romano_openmc:_2015},
OpenMOC\cite{boyd_openmoc_2014}, and
PyNE\cite{bates_pyne_2014,biondo_quality_2014}.''

>>>>

        More recently, Aufiero et al. \cite{aufiero_development_2014} have 
        begun to
        approach transient simulations in the MSFR within the finite 
        volume
        OpenFOAM multiphysics toolkit \cite{weller_tensorial_1998}.  This 
        approach
        benefits from pre-implemented turbulence models available in the 
        OpenFOAM
        library and captures the full-core three-dimensional geometry of the 
        reactor
        primary circuit.  OpenFOAM CFD has additionally been shown by 
        Laureau et
        al. \cite{laureau_transient_2017} to couple well with Transient Fission 
        Matrix
        neutronics within the MSFR.
\end{solution}

@@

\question Concerning the openness of the code and the possibility to contribute to it, it should be noted that codes solving for neutron transport can be subject to export restrictions (following their potential dual use), and in principle all contributors should get an export control authorization from their own country. The authors are not strictly required to change the manuscript, but they may consider mentioning the fact that the openness of a nuclear code can be somewhat thwarted by national and international laws.
\begin{solution}
	Excellent point. We have added the following text: ``While export
control laws have the potential to restrict openness of neutron transport
software that is dual use, there is no reason to believe that Moltres could be
used for weapons proliferation.  Moltres requires that cross sections be
provided by the user, implements a combination of algorithms that can be easily
derived from open literature, is tailored to molten salt reactor physics.
Accordingly, Moltres joins a veritable parade of open academic nuclear
engineering software such as OpenMC \cite{romano_openmc:_2015},
OpenMOC \cite{boyd_openmoc_2014}, and
PyNE \cite{bates_pyne_2014,biondo_quality_2014}.''
